Supplementary Information

### 2020-08-27 doc/manuscript/MEE_manuscript_SI.Rmd
update SI

In either case we need bark thickness--ideally allometries describing the relationship between DBH and bark thickness. 
This is especially critical for thick-barked species
When bark thickness data were available, we generated allometries ... 
lognormal model with intercept forced to zero: lm(bark_depth.mm ~ -1 + log(dbh_no_bark.cm+1):bark_species, data = bark)
([issue #8 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/8))

@@

\newpage
## Table S4. Frequency of $DBH$-climate interactions across all sites and growth metrics
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_raw <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climate_interactions_summary.csv", stringsAsFactors = FALSE, check.names = FALSE)
#this reads in the table, but knit fails if I try to render it (probably because of underscores). It also needs ot be rearranged
#kable(table_raw, format = "latex", booktabs = TRUE, caption = "Table S  . Frequency of DBH-climate interactions", escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position")) 
```

>>>>

In either case we need bark thickness--ideally allometries describing the relationship between DBH and bark thickness (Table S4). 
This is especially critical for thick-barked species
When bark thickness data were available, we generated allometries ... 
lognormal model with intercept forced to zero: lm(bark_depth.mm ~ -1 + log(dbh_no_bark.cm+1):bark_species, data = bark)
([issue #8 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/8))

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
allometries_table <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO_dendro/data_processed/dbh_to_bark_allometries_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
#kable(allometries_table, format = "latex", booktabs = TRUE,   escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

\newpage
## Table S5. Frequency of $DBH$-climate interactions across all sites and growth metrics
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
table_raw <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/results/climate_interactions_summary.csv", stringsAsFactors = FALSE, check.names = FALSE)
#this reads in the table, but knit fails if I try to render it (probably because of underscores). It also needs ot be rearranged
#kable(table_raw, format = "latex", booktabs = TRUE, caption = "Table S  . Frequency of DBH-climate interactions", escape = F)%>%
#  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
